Supplementary Figures and Tables

### 2020-11-05 Reproducible_codes_Supp_figures.Rmd
supplement_fig_codes
tidyverse styling and validating code

```{r, include=FALSE}
data("minsamp") # refers Sample and Sample+ data
```

See Table S1 in Supplementary Figures and Tables file.

@@

```{r, message=FALSE, warning=FALSE}
priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression)%>%
  update_how("Gene2", 2)
```

@@

priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression)%>%
  update_how("Gene2", 2)%>%
  simulate(cycle= 2)

@@

```{r, message=FALSE, warning=FALSE}
priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression)%>%
  update_how("Gene2", 2)%>%
  simulate(2)%>%
  activate(edges)%>%
  as_tibble()%>%
  select(Competing_name,comp_count_list,effect_list)%>%
  unnest()
```

@@

```{r, message=FALSE, warning=FALSE}
priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression, aff_factor = c(energy, seed_type), deg_factor = region)

priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression, aff_factor = c(energy, seed_type), deg_factor = region)%>%
  update_how("Gene2", 2)
```

priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression, aff_factor = c(energy, seed_type), deg_factor = region)%>%
  update_how("Gene2", 2)%>%
  simulate(cycle=2)
```

@@

```{r, message=FALSE, warning=FALSE}
priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression, aff_factor = c(energy, seed_type), deg_factor = region)%>%
  update_how("Gene2", 2)%>%
  simulate(3)%>%
  activate(edges)%>%
  as_tibble()%>%
  select(Competing_name,comp_count_list,effect_list)%>%
  unnest()
```

@@

priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression, aff_factor = c(energy, seed_type), deg_factor = region)%>%
  update_how("Gene4", 2)%>%
  simulate(cycle = 2)
```

@@

```{r, message=FALSE, warning=FALSE}
priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression, aff_factor = c(energy, seed_type), deg_factor = region)%>%
  update_how("Gene4", 2)%>%
  simulate(3)%>%
  activate(edges)%>%
  as_tibble()%>%
  select(Competing_name,comp_count_list,effect_list)%>%
  unnest()
```

>>>>

```{r, include=FALSE}
data("minsamp") # refers to Sample and Sample+ data
```

See Table S1 in Supplementary Figure and Table file.

@@

```{r, message=FALSE, warning=FALSE}
priming_graph(minsamp, 
              competing_count = Competing_expression, 
              miRNA_count = miRNA_expression) %>%
  update_how("Gene2", 2)
```

@@

priming_graph(minsamp, 
              competing_count = Competing_expression, 
              miRNA_count = miRNA_expression) %>%
  update_how("Gene2", 2) %>%
  simulate(cycle = 2)
```

@@

```{r, message=FALSE, warning=FALSE}
priming_graph(minsamp, 
              competing_count = Competing_expression, 
              miRNA_count = miRNA_expression) %>%
  update_how("Gene2", 2) %>%
  simulate(2) %>%
  activate(edges) %>%
  as_tibble() %>%
  select(Competing_name, comp_count_list, effect_list) %>%
  unnest()
```

@@

```{r, message=FALSE, warning=FALSE}
priming_graph(minsamp, 
              competing_count = Competing_expression, 
              miRNA_count = miRNA_expression, 
              aff_factor = c(energy, seed_type), 
              deg_factor = region)
```

```{r, message=FALSE, warning=FALSE}
priming_graph(minsamp, 
              competing_count = Competing_expression, 
              miRNA_count = miRNA_expression, 
              aff_factor = c(energy, seed_type), 
              deg_factor = region) %>%
  update_how("Gene2", 2)
```

```{r, message=FALSE, warning=FALSE}
priming_graph(minsamp, 
              competing_count = Competing_expression, 
              miRNA_count = miRNA_expression, 
              aff_factor = c(energy, seed_type), 
              deg_factor = region) %>%
  update_how("Gene2", 2) %>%
  simulate(cycle = 2)
```

@@

```{r, message=FALSE, warning=FALSE}
priming_graph(minsamp, 
              competing_count = Competing_expression, 
              miRNA_count = miRNA_expression, 
              aff_factor = c(energy, seed_type), 
              deg_factor = region) %>%
  update_how("Gene2", 2) %>%
  simulate(3) %>%
  activate(edges) %>%
  as_tibble() %>%
  select(Competing_name, comp_count_list, effect_list) %>%
  unnest()
```

@@

```{r, message=FALSE, warning=FALSE}
priming_graph(minsamp, 
              competing_count = Competing_expression, 
              miRNA_count = miRNA_expression, 
              aff_factor = c(energy, seed_type), 
              deg_factor = region) %>%
  update_how("Gene4", 2) %>%
  simulate(cycle = 2)
```

@@

```{r, message=FALSE, warning=FALSE}
priming_graph(minsamp, 
              competing_count = Competing_expression, 
              miRNA_count = miRNA_expression, 
              aff_factor = c(energy, seed_type), 
              deg_factor = region) %>%
  update_how("Gene4", 2) %>%
  simulate(3) %>%
  activate(edges) %>%
  as_tibble() %>%
  select(Competing_name, comp_count_list, effect_list) %>%
  unnest()
```

### 2020-11-05 Supplementary_fig_tab.Rmd
tidyverse styling and validating code

```{r, message=FALSE, warning=FALSE,echo=FALSE, fig.cap= "Sample Dataset in Steady-state. Inıtial expression levels in minsamp network (*Sample* network in manuscript). The network contains two miRNAs and 6 genes with arbitrarily chosen expression values. Refer to Table S1 for exact expression values", fig.width=5, fig.height=4}
priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression)%>%
  vis_graph(Competing_color = "navajowhite3", mirna_color = "ivory4",
            title = " ")+
  geom_node_text(aes(label = name), repel = TRUE, size =3)
```

```{r, message=FALSE, warning=FALSE,echo=FALSE,  fig.keep='all', fig.cap= "Gene2 Upregulation on Sample Dataset. Expression level of Gene2 is increased from 10,000 to 20,000 in order to demonstrate the calculation steps.", fig.width=5, fig.height=4}
priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression)%>%
  update_how("Gene2", 2)%>%
  vis_graph(Competing_color = "navajowhite3", mirna_color = "ivory4", Upregulation = "red", 
            title = " ")+
  geom_node_text(aes(label = name), repel = TRUE, size =3)
```

@@

priming_graph(minsamp, 
              competing_count = Competing_expression, 
              miRNA_count = miRNA_expression)%>%
  update_how("Gene2", 2)%>%
  simulate(2)%>%
  vis_graph(Competing_color = "navajowhite3", 
            mirna_color = "ivory4", 
            Upregulation = "red", 
            Downregulation = "blue", 
            title = "B")+
  geom_node_text(aes(label = name), repel = TRUE, size =3)

@@

```{r, message=FALSE, warning=FALSE, echo=FALSE, fig.cap= "Sample+ in Steady-state. Interaction factors of Sample+ network are available in Table S1.", fig.width=5, fig.height=4}
priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression, aff_factor = c(energy, seed_type), deg_factor = region)%>%
  vis_graph(Competing_color = "navajowhite3", mirna_color = "ivory4", 
            title = " ")+
  geom_node_text(aes(label = name), repel = TRUE, size =3)

```{r, message=FALSE, warning=FALSE, echo=FALSE,  fig.cap= "Perturbation in Sample+ network by two-fold increase in Gene2 expression level.", fig.width=5, fig.height=4}
priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression, aff_factor = c(energy, seed_type), deg_factor = region)%>%
  update_how("Gene2", 2)%>%
  vis_graph(Competing_color = "navajowhite3", mirna_color = "ivory4", Upregulation = "red", 
            title = " ")+
  geom_node_text(aes(label = name), repel = TRUE, size =3)
```

```{r, message=FALSE, warning=FALSE,echo=FALSE, out.width='50%', fig.asp=1, fig.ncol = 2, fig.show='hold', fig.cap = "Sequential iteration of Sample+ A) First response of system to Gene2 upregulation (2nd iteration). B) Spreading of perturbation on system (3rd iteration). Although visualisation looks similar to Figure S4B, current counts of genes are drastically different."}
priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression, aff_factor = c(energy, seed_type), deg_factor = region)%>%
  update_how("Gene2", 2)%>%
  simulate(cycle = 1)%>%
  vis_graph(Competing_color = "navajowhite3", mirna_color = "ivory4", Upregulation = "red", Downregulation = "blue", title = "A")+
  geom_node_text(aes(label = name), repel = TRUE, size =3)

priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression, aff_factor = c(energy, seed_type), deg_factor = region)%>%
  update_how("Gene2", 2)%>%
  simulate(cycle = 2)%>%
  vis_graph(Competing_color = "navajowhite3", mirna_color = "ivory4", Upregulation = "red", Downregulation = "blue", title = "B")+
  geom_node_text(aes(label = name), repel = TRUE, size =3)

@@

priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression, aff_factor = c(energy, seed_type), deg_factor = region)%>%
  vis_graph(Competing_color = "navajowhite3", mirna_color = "ivory4", Upregulation = "red", title = "A")+
  geom_node_text(aes(label = name), repel = TRUE, size =3)

priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression, aff_factor = c(energy, seed_type), deg_factor = region)%>%
  update_how("Gene4", 2)%>%
  vis_graph(Competing_color = "navajowhite3", mirna_color = "ivory4", Upregulation = "red", title = "B")+
  geom_node_text(aes(label = name), repel = TRUE, size =3)

priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression, aff_factor = c(energy, seed_type), deg_factor = region)%>%
  update_how("Gene4", 2)%>%
  simulate(cycle=1)%>%
  vis_graph(Competing_color = "navajowhite3", mirna_color = "ivory4", Upregulation = "red", title = "C")+
  geom_node_text(aes(label = name), repel = TRUE, size =3)

priming_graph(minsamp, competing_count = Competing_expression, miRNA_count = miRNA_expression, aff_factor = c(energy, seed_type), deg_factor = region)%>%
  update_how("Gene4", 2)%>%
  simulate(cycle=2)%>%
  vis_graph(Competing_color = "navajowhite3", mirna_color = "ivory4", Upregulation = "red", title = "D")+
  geom_node_text(aes(label = name), repel = TRUE, size =3)
```

@@

matched_patient_exp_dataset <- readRDS("figures_manuscript/matched_patient_exp_dataset.RDS")
mirtarbase_gene_res <- readRDS("figures_manuscript/mirtarbase_gene_res.RDS")

matched_patient_exp_dataset%>%
  filter(Ensembl_Gene_Id %in% pull(filter(mirtarbase_gene_res, situ == "tumor_specific"), Ensembl_Gene_Id))%>%
  pivot_longer(cols = contains("TCGA"), names_to="patient_id", values_to = "expressions")%>%
  mutate(patient = ifelse(endsWith(patient_id, "01A"), "tumor", "normal"))%>%
  left_join(mirtarbase_gene_res, by ="Ensembl_Gene_Id")%>%
  group_by(patient, Ensembl_Gene_Id)%>%
  ggplot(aes(x= hgnc_symbol, y=log2(expressions), fill = patient))+
  #scale_y_log10()+
  geom_boxplot(position = "dodge")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90), panel.background = element_rect())+
  xlab("")
```

@@

```{r, eval=FALSE, include=FALSE}
library(xtable)
knitr::opts_chunk$set(tidy.opts=list(width.cutoff=50),tidy=TRUE)
library(gt)
knitr::opts_chunk$set(cache=FALSE)

>>>>

```{r, message=FALSE, warning=FALSE,echo=FALSE, fig.cap= "Sample Dataset in Steady-state. Inıtial expression levels in minsamp network (*Sample* network in manuscript). The network contains two miRNAs and 6 genes with arbitrarily chosen expression values. Refer to Table S1 for exact expression values", fig.width=5, fig.height=4}
priming_graph(minsamp, 
              competing_count = Competing_expression, 
              miRNA_count = miRNA_expression) %>%
  vis_graph(Competing_color = "navajowhite3", 
            mirna_color = "ivory4",
            title = " ") +
  geom_node_text(aes(label = name), repel = TRUE, size = 3)
```

```{r, message=FALSE, warning=FALSE,echo=FALSE,  fig.keep='all', fig.cap= "Gene2 Upregulation on Sample Dataset. Expression level of Gene2 is increased from 10,000 to 20,000 in order to demonstrate the calculation steps.", fig.width=5, fig.height=4}
priming_graph(minsamp,
              competing_count = Competing_expression,
              miRNA_count = miRNA_expression) %>%
  update_how("Gene2", 2) %>%
  vis_graph(Competing_color = "navajowhite3", 
            mirna_color = "ivory4", 
            Upregulation = "red",
            title = " ") +
  geom_node_text(aes(label = name), repel = TRUE, size = 3)
```

@@

priming_graph(minsamp, 
              competing_count = Competing_expression, 
              miRNA_count = miRNA_expression) %>%
  update_how("Gene2", 2) %>%
  simulate(2) %>%
  vis_graph(Competing_color = "navajowhite3", 
            mirna_color = "ivory4", 
            Upregulation = "red", 
            Downregulation = "blue", 
            title = "B")+
  geom_node_text(aes(label = name), repel = TRUE, size =3)

@@

```{r, message=FALSE, warning=FALSE, echo=FALSE, fig.cap= "Sample+ in Steady-state. Interaction factors of Sample+ network are available in Table S1.", fig.width=5, fig.height=4}
priming_graph(minsamp, 
              competing_count = Competing_expression, 
              miRNA_count = miRNA_expression, 
              aff_factor = c(energy, seed_type), 
              deg_factor = region) %>%
  vis_graph(Competing_color = "navajowhite3", 
            mirna_color = "ivory4",
            title = " ") +
  geom_node_text(aes(label = name), repel = TRUE, size = 3)
```

```{r, message=FALSE, warning=FALSE, echo=FALSE,  fig.cap= "Perturbation in Sample+ network by two-fold increase in Gene2 expression level.", fig.width=5, fig.height=4}
priming_graph(minsamp, 
              competing_count = Competing_expression, 
              miRNA_count = miRNA_expression, 
              aff_factor = c(energy, seed_type), 
              deg_factor = region) %>%
  update_how("Gene2", 2) %>%
  vis_graph(Competing_color = "navajowhite3", 
            mirna_color = "ivory4", 
            Upregulation = "red",
            title = " ") +
  geom_node_text(aes(label = name), repel = TRUE, size = 3)
```

```{r, message=FALSE, warning=FALSE,echo=FALSE, out.width='50%', fig.asp=1, fig.ncol = 2, fig.show='hold', fig.cap = "Sequential iteration of Sample+ A) First response of system to Gene2 upregulation (2nd iteration). B) Spreading of perturbation on system (3rd iteration). Although visualisation looks similar to Figure S4B, current counts of genes are drastically different."}
priming_graph(minsamp, 
              competing_count = Competing_expression, 
              miRNA_count = miRNA_expression, 
              aff_factor = c(energy, seed_type), 
              deg_factor = region) %>%
  update_how("Gene2", 2) %>%
  simulate(cycle = 1) %>%
  vis_graph(Competing_color = "navajowhite3", 
            mirna_color = "ivory4", 
            Upregulation = "red", 
            Downregulation = "blue", 
            title = "A") +
  geom_node_text(aes(label = name), repel = TRUE, size = 3)

priming_graph(minsamp, 
              competing_count = Competing_expression, 
              miRNA_count = miRNA_expression, 
              aff_factor = c(energy, seed_type), 
              deg_factor = region) %>%
  update_how("Gene2", 2) %>%
  simulate(cycle = 2) %>%
  vis_graph(Competing_color = "navajowhite3", 
            mirna_color = "ivory4", 
            Upregulation = "red", 
            Downregulation = "blue", 
            title = "B") +
  geom_node_text(aes(label = name), repel = TRUE, size = 3)
```

@@

priming_graph(minsamp, 
              competing_count = Competing_expression, 
              miRNA_count = miRNA_expression, 
              aff_factor = c(energy, seed_type), 
              deg_factor = region) %>%
  vis_graph(Competing_color = "navajowhite3", 
            mirna_color = "ivory4", 
            Upregulation = "red", 
            title = "A") +
  geom_node_text(aes(label = name), repel = TRUE, size =3)

priming_graph(minsamp, 
              competing_count = Competing_expression, 
              miRNA_count = miRNA_expression, 
              aff_factor = c(energy, seed_type), 
              deg_factor = region) %>%
  update_how("Gene4", 2) %>%
  vis_graph(Competing_color = "navajowhite3", 
            mirna_color = "ivory4", 
            Upregulation = "red", 
            title = "B") +
  geom_node_text(aes(label = name), repel = TRUE, size =3)

priming_graph(minsamp, 
              competing_count = Competing_expression, 
              miRNA_count = miRNA_expression, 
              aff_factor = c(energy, seed_type), 
              deg_factor = region) %>%
  update_how("Gene4", 2) %>%
  simulate(cycle=1) %>%
  vis_graph(Competing_color = "navajowhite3", 
            mirna_color = "ivory4", 
            Upregulation = "red", 
            title = "C") +
  geom_node_text(aes(label = name), repel = TRUE, size =3)

priming_graph(minsamp, 
              competing_count = Competing_expression, 
              miRNA_count = miRNA_expression, 
              aff_factor = c(energy, seed_type), 
              deg_factor = region) %>%
  update_how("Gene4", 2) %>%
  simulate(cycle=2) %>%
  vis_graph(Competing_color = "navajowhite3", 
            mirna_color = "ivory4", 
            Upregulation = "red", 
            title = "D") +
  geom_node_text(aes(label = name), repel = TRUE, size =3)
```

@@

matched_patient_exp_dataset <- readRDS("figure_manuscript/matched_patient_exp_dataset.RDS")
mirtarbase_gene_res <- readRDS("figure_manuscript/mirtarbase_gene_res.RDS")

matched_patient_exp_dataset %>%
  filter(Ensembl_Gene_Id %in% pull(filter(mirtarbase_gene_res, situ == "tumor_specific"), Ensembl_Gene_Id)) %>%
  pivot_longer(cols = contains("TCGA"), 
               names_to = "patient_id", 
               values_to = "expressions") %>%
  mutate(patient = ifelse(endsWith(patient_id, "01A"), 
                          "tumor", "normal")) %>%
  left_join(mirtarbase_gene_res, by = "Ensembl_Gene_Id") %>%
  group_by(patient, Ensembl_Gene_Id) %>%
  ggplot(aes(x = hgnc_symbol, y = log2(expressions), fill = patient)) +
  # scale_y_log10()+
  geom_boxplot(position = "dodge") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90), 
        panel.background = element_rect()) +
  xlab("")
```

@@
